---
title: "2022_pond_factors"
author: "HEK"
date: "2023_12_11"
---

# MSH 2022 Thermal Refuges

Load Data

Distributions of TRQ and Temperature

Linear Models

1)  Summer TRQ

2)  Heatwave TRQ

3)  Summer Temperature

4)  Heatwave Temperature

4-Panel Figure

## Load Data

```{r, echo = `FALSE`}
library(readr)
library(gridExtra)
library(reshape2)
library(gridExtra)
library(purrr)
library(RColorBrewer)
library(lubridate)
library(tidyverse)
library(tidyr)
#library(insol)
library(grid)
library(forcats)
library(scales)
library(moderndive)
library(ggpubr)
library(corrplot)
library(MuMIn)
library(data.table)
library(dplyr)
library(ggplot2)
#load the car library
library(car)
library(ggpubr)
#library(cowplot)

# Reset global environment
rm(list=ls())

#individual regression models
setwd("/home/feys/MSH/hannahk_practice1/SF Concept 2023 - hannah")
factors_1 <- read_csv("factors_1.csv")

# read in volume draw down data
volume_DD_data <- read_csv("volume_drawdown.csv")
# replace columns
factors_no_DD <-
  subset(factors_1,
         select = -c(surface_area, volume, sa_v_ratio, DD_Slope, DD_Yint, perDD))
factors_new_vol <- cbind(factors_no_DD, volume_DD_data[, 2:6])
factors_new_vol <- factors_new_vol %>%
  mutate(sa_v_ratio=surface_area_m/initial_vol)  %>%
  dplyr::rename(surface_area=surface_area_m, volume=initial_vol, DD_Slope=slope, DD_Yint=yint)


factors <- factors_new_vol

#change vegetation from qualitative to quant
factors <- factors %>% mutate(
  sub_v = case_when(
    submerged_vol == "low" ~ 1, 
    submerged_vol == "moderate" ~2, 
    submerged_vol == "high" ~3),
  sub_cov = case_when(
    submerged_cov == "low" ~ 1, 
    submerged_cov == "moderate" ~2, 
    submerged_cov == "high" ~3
  ))


#select quant data
factorsnum <- factors %>% dplyr::select(pond,T_avg, DO_avg, SPC_avg, pH_avg, FNU_avg, 
                                 surface_area, volume, sa_v_ratio, altitude, canopy, 
                                 catchment, draw_r, emergent, 
                                 sub_cov, sub_v, depth, overhanging, surface,
                                 meanT_HW_bottom,meanT_HW_surface,meanT_HW,meanT,meanT_bottom,
                                 meanT_surface,TR,HW_TR, DD_Slope, DD_Yint, perDD, pond)
#make names shorter
factorsnum <- factorsnum %>% dplyr::rename(TempSpot=T_avg,DO = DO_avg,
                                    SPC = SPC_avg, pH= pH_avg,
                                    FNU = FNU_avg, SA = surface_area,
                                    V = volume, SAV = sa_v_ratio,
                                    A = altitude, CC = canopy,
                                    CA = catchment,
                                    DR = draw_r,
                                     EV = emergent,
                                    SVV = sub_v, SVC = sub_cov, D = depth,
                                    OV=overhanging, SV = surface,
                                    H_TRQ=HW_TR, TRQ= TR,
                                    meanT_HW_bottom=meanT_HW_bottom,meanT_HW_surface=meanT_HW_surface,
                                    meanT_HW= meanT_HW , meanT=meanT,
                                    meanT_bottom= meanT_bottom,meanT_surface = meanT_surface, DD_Slope=DD_Slope,
                                    DD_Yint=DD_Yint, perDD=perDD
                                    )


factorsnum <-factorsnum %>% dplyr::select (-"pond")
```

## 0) TRQ & Temp Distributions

### 0.1) Mean Pond Temperature & TRQ

```{r}

library(hrbrthemes)
temp_binwidth <- 1
trq_binwidth <- temp_binwidth/16
fonts <- 12

# SUMMER TRQ

summer_TRQ_df <- factorsnum %>% drop_na(TRQ) %>% dplyr::select(TRQ) %>% pivot_longer(1,names_to="Metric",values_to = "Value")  # retrieve mean summer TRQs for each pond

## histogram of mean summer TRQs 
summer_trq_hist <- ggplot(summer_TRQ_df,aes(x=Value,fill=Metric,color=Metric,))+
  geom_density(aes(y=after_stat(density)* (nrow(summer_TRQ_df) * trq_binwidth)),alpha=0.4,stat="density",color="#e9ecef")+
  geom_histogram(aes(y=after_stat(count)),position="identity", color="#e9ecef", alpha=0.7,binwidth=trq_binwidth)+
  coord_cartesian(xlim=c(0,1))+
  scale_fill_manual(values=c("#2C9CB0")) +
  theme_light()+
  theme(legend.position = "none",axis.title.y = element_blank(),axis.title.x = element_blank(),plot.title = element_text(hjust = 0.5)
        #,plot.tag.position = c(0.085, .95)
        ,plot.tag = element_text(size = fonts)
        )+
  labs(tag = "A")

# HEATWAVE TRQ
heatwave_TRQ_df <- factorsnum %>% drop_na(H_TRQ) %>% dplyr::select(H_TRQ) %>% pivot_longer(1,names_to="Metric",values_to = "Value") # retrieve mean TRQs for each pond during heatwave conditions

## histogram of mean TRQs during heatwave conditions
heatwave_trq_summary <- heatwave_TRQ_df %>% summarise(max_HW_TRQ = max(Value), min_HW_TRQ = min(Value), median_HW_TRQ = median(Value))
#plot data
heatwave_trq_hist <- ggplot(heatwave_TRQ_df,aes(x=Value,fill=Metric,color=Metric))+
  geom_density(aes(y=after_stat(density)* (nrow(summer_TRQ_df) * trq_binwidth)),alpha=0.4,stat="density",color="#e9ecef")+
  geom_histogram(aes(y=after_stat(count)),position="identity", color="#e9ecef", alpha=0.7,binwidth=trq_binwidth)+
  scale_fill_manual(values=c("#F06C00")) +
  coord_cartesian(xlim=c(0,1))+
  theme_light()+
  xlab("Thermal Refuge Quality")+
  theme(legend.position = "none",axis.title.y = element_blank(),plot.title = element_text(hjust = 0.4),axis.title.x = element_text(size=fonts)
        #,plot.tag.position = c(0.085, .95)
        ,plot.tag = element_text(size = fonts)
        )+
  labs(tag = "C")

#heatwave_trq_hist


temp_df <- factorsnum %>% drop_na(meanT,meanT_HW) %>% dplyr::select(meanT,meanT_HW) %>% pivot_longer(1:2,names_to="Metric",values_to = "Value") 



# SUMMER TEMP
summer_temp_df <- factorsnum %>% drop_na(meanT) %>% dplyr::select(meanT) %>% pivot_longer(1,names_to="Metric",values_to = "Value") # retrieve mean summer temperatures for each pond

summer_temp_summary <- summer_temp_df %>% summarise(max_S_T = max(Value), min_S_T = min(Value), median_S_T = median(Value)) # calculate stats on summer temp

## histogram of mean summer temperatures
summer_temp_hist <- ggplot(summer_temp_df,aes(x=Value,fill=Metric,color=Metric,))+
  geom_density(aes(y=after_stat(density)* (nrow(summer_temp_df) * temp_binwidth)),alpha=0.4,stat="density",color="#e9ecef")+
  geom_histogram(aes(y=after_stat(count)),position="identity", color="#e9ecef", alpha=0.7,binwidth=temp_binwidth)+
  scale_fill_manual(values=c("#2C9CB0")) +
  theme_light()+
  coord_cartesian(xlim=c(10,26))+
  theme(legend.position = "none",axis.title.y = element_blank(),axis.title.x = element_blank(),axis.text.y = element_blank(), axis.ticks.y = element_blank(),plot.title = element_text(hjust = 0.5)
        #,plot.tag.position = c(0.055, .95)
        ,plot.tag = element_text(size = fonts)
        )+
  labs(tag = "B")

#summer_temp_hist

# HEATWAVE TEMP
heatwave_temp_df <- factorsnum %>% drop_na(meanT_HW) %>% dplyr::select(meanT_HW) %>% pivot_longer(1,names_to="Metric",values_to = "Value") # retrieve mean temperatures for each pond during heatwave conditions

heatwave_temp_summary <- heatwave_temp_df %>% summarise(max_HW_T = max(Value), min_HW_T = min(Value), median_HW_T = median(Value)) # stats for heatwave temperatures

## histogram of mean temperatures during heatwave conditions
heatwave_temp_hist <- ggplot(heatwave_temp_df,aes(x=Value,fill=Metric,color=Metric,))+
  geom_density(aes(y=after_stat(density)* (nrow(heatwave_temp_df) * temp_binwidth)),alpha=0.4,stat="density",color="#e9ecef")+
  geom_histogram(aes(y=after_stat(count)),position="identity", color="#e9ecef", alpha=0.7,binwidth=temp_binwidth)+
  scale_fill_manual(values=c("#F06C00")) +
  theme_light()+
  coord_cartesian(xlim=c(10,26))+
  xlab("Mean Pond Temp (°C)")+
  theme(legend.position = "none",axis.title.y = element_blank(),axis.text.y = element_blank(), axis.ticks.y = element_blank(),plot.title = element_text(hjust = 0.5),axis.title.x = element_text(size=fonts),
        #plot.tag.position = c(0.055, .95),
        plot.tag = element_text(size = fonts)
        )+
  labs(tag = "D")

# Make grid of all 4 histograms

hist_plots_arrange <- grid.arrange(summer_trq_hist,
                                   summer_temp_hist,
                                   heatwave_trq_hist,
                                   heatwave_temp_hist, 
                                   left = grid::textGrob("Count", x = .5, hjust = .3, rot = 90,gp = gpar(fontsize = 13)), 
                                   right = grid::textGrob("Summer                                Heatwave", x = .3, hjust = .51, rot = 270,gp = gpar(fontsize = 13)))

ggsave("hist_plots_arrange3.pdf", plot= hist_plots_arrange,width = 16, height = 12, units = "cm")

```

``` {#summer_trq_hist}
```

## Factor Plot Code

```{r}




```

### 0.2) Mean Surface/Bottom Temperatures

```{r}
#plot distribution of mean temp and TRQ



########## Surface

# Surface Summer
surface_hist_df <- factorsnum %>% drop_na(meanT_surface) %>% dplyr::select(meanT_surface) %>% pivot_longer(1,names_to="Metric",values_to = "Value") # retrieve entire summer surface temps for each pond

#plot data
surface_binwidth <- 12.8/15
# histogram of the entire summer mean pond temperatures
surface_hist_plot <- ggplot(surface_hist_df,aes(x=Value,fill=Metric,color=Metric,))+
  geom_density(aes(y=after_stat(density)* (nrow(surface_hist_df) * surface_binwidth)),alpha=0.4,stat="density",color="#e9ecef")+
  geom_histogram(aes(y=after_stat(count)),position="identity", color="#e9ecef", alpha=0.7,binwidth=surface_binwidth)+
  coord_cartesian(xlim=c(13.6,26.4),ylim=c(0,5))+
  scale_x_continuous(breaks=c(14,18,22,26))+
  scale_fill_manual(values=c("#EB2E28")) +
  theme_light()+
  theme(legend.position = "none",axis.title.y = element_blank(),axis.title.x = element_blank(),plot.title = element_text(hjust = 0.5))+
  labs(title="Summer Surface",fill="")

#surface_hist_plot


# Surface Heatwave
surface_HW_hist_df <- factorsnum %>% drop_na(meanT_HW_surface) %>% dplyr::select(meanT_HW_surface) %>% pivot_longer(1,names_to="Metric",values_to = "Value") # retrieve entire heatwave surface temps for each pond

# histogram of mean pond temperatures during heatwave conditions
surface_HW_hist_plot <- ggplot(surface_HW_hist_df,aes(x=Value,fill=Metric,color=Metric,))+
  geom_density(aes(y=after_stat(density)* (nrow(surface_HW_hist_df) * surface_binwidth)),alpha=0.4,stat="density",color="#e9ecef")+
  geom_histogram(aes(y=after_stat(count)),position="identity", color="#e9ecef", alpha=0.7,binwidth=surface_binwidth)+
  coord_cartesian(xlim=c(13.6,26.4),ylim=c(0,5))+
  scale_x_continuous(breaks=c(14,18,22,26))+
  scale_fill_manual(values=c("#EB2E28")) +
  theme_light()+
  theme(legend.position = "none",axis.title.y = element_blank(),axis.title.x = element_blank(),plot.title = element_text(hjust = 0.5))+
  labs(title="Heatwave Surface",fill="")

########## Bottom

# Bottom Summer
bottom_hist_df <- factorsnum %>% drop_na(meanT_bottom) %>% dplyr::select(meanT_bottom) %>% pivot_longer(1,names_to="Metric",values_to = "Value") # retrieve entire summer bottom temps for each pond

## histogram of mean pond bottom temperatures during entire summer
benthic_binwidth <- 1

bottom_hist_plot <- ggplot(bottom_hist_df,aes(x=Value,fill=Metric,color=Metric,))+
  geom_density(aes(y=after_stat(density)* (nrow(bottom_hist_df) * benthic_binwidth)),alpha=0.4,stat="density",color="#e9ecef")+
  geom_histogram(aes(y=after_stat(count)),position="identity", color="#e9ecef", alpha=0.7,binwidth=benthic_binwidth)+
  coord_cartesian(xlim=c(10,25),ylim=c(0,5))+
  scale_fill_manual(values=c("#5008FC")) +
  theme_light()+
  theme(legend.position = "none",axis.title.y = element_blank(),axis.title.x = element_blank(),plot.title = element_text(hjust = 0.5),axis.text.y = element_blank(), axis.ticks.y = element_blank())+
  labs(title="Summer Benthic",fill="")

#surface_hist_plot


# Bottom Heatwave
bottom_HW_hist_df <- factorsnum %>% drop_na(meanT_HW_bottom) %>% dplyr::select(meanT_HW_bottom) %>% pivot_longer(1,names_to="Metric",values_to = "Value") # retrieve mean bottom temps for each pond during heatwave conditions

## histogram of mean pond bottom temperatures during heatwave conditions
bottom_HW_hist_plot <- ggplot(bottom_HW_hist_df,aes(x=Value,fill=Metric,color=Metric,))+
  geom_density(aes(y=after_stat(density)* (nrow(bottom_HW_hist_df) * benthic_binwidth)),alpha=0.4,stat="density",color="#e9ecef")+
  geom_histogram(aes(y=after_stat(count)),position="identity", color="#e9ecef", alpha=0.7,binwidth=benthic_binwidth)+
  coord_cartesian(xlim=c(10,25),ylim=c(0,5))+
  scale_fill_manual(values=c("#5008FC")) +
  theme_light()+
  theme(legend.position = "none",axis.title.y = element_blank(),axis.text.y = element_blank(), axis.ticks.y = element_blank(),axis.title.x = element_blank(),plot.title = element_text(hjust = 0.5))+
  labs(title="Heatwave Benthic",fill="")

# Plot all 4 in one multipanel figure
yleft <- textGrob("Count", rot = 90, gp = gpar(fontsize = 12))
si_x_title <- textGrob("Temperature (°C)", gp = gpar(fontsize = 12))

surface_bottom_plots_grid <- grid.arrange(surface_hist_plot,bottom_hist_plot,surface_HW_hist_plot,bottom_HW_hist_plot, left = yleft,bottom=si_x_title)
ggsave("SI_temp_fig.pdf", plot= surface_bottom_plots_grid,width = 20, height = 15, units = "cm")
```

For each model (TRQ - Entire Summer, TRQ - Heatwave Conditions, Temperature - Entire Summer, Temperature - Heatwave Conditions)

## 1) Summer TRQ

### Model Selection

```{r, echo = `FALSE`}
##########################################################################################
##
##########################################################################################

# Retrieve Pond Data with TRQ
modfactors_trqS <- factorsnum %>% drop_na(TRQ)
# Scale all factors
modfactors_trqS_scaled<- modfactors_trqS %>% mutate_if(is.numeric, scale)%>% drop_na(TRQ) 


# Linear Model for TRQ over the summer
refmodm<-lm(TRQ ~ perDD + SV + meanT + FNU + CC + CA + V, data=modfactors_trqS_scaled)


# Plot VIF values
vif_trqS<-vif(refmodm)
vif_trqS_df <- tibble::rownames_to_column(data.frame(vif_trqS), "coefficient")
ggplot(vif_trqS_df, aes(x=coefficient, y=vif_trqS)) +
  coord_flip()+
  geom_bar(stat = "identity")+
  geom_hline(yintercept = 5.0,linetype="dashed", color = "red")


```

### Model Residuals

```{r, echo = `FALSE`}
###############################################################################################
shapiro.test(rstandard(refmodm)) #low p-value indicates that the observed data is unlikely under the assumption it was drawn from a normal distribution.
# Check for normality of residuals
modfactors_trqS_scaled$residual <- refmodm$residuals
# check model residuals
test1<-qplot(refmodm$fitted, refmodm$residuals,
      geom = "point") +
  geom_abline(intercept = 0,
              slope = 0,
              colour = "red") +
  labs(title = "Plot of residuals vs fitted values",
       x = "fitted value",
       y = "residual")
# Make a histogram of the residuals
test2<- qplot(refmodm$residuals,
              geom = "histogram",
              bins = 10) +
  labs(title = "Histogram of residuals",
       x = "residual")
test3<-ggplot(data = modfactors_trqS_scaled, aes(sample = residual)) +
  geom_qq() +
  geom_qq_line(colour = "red") +
  labs(title = "Quantile plot of residuals")
grid.arrange(test1,test2,test3)
###############################################################################################
```

### Model Results

```{r, echo = `FALSE`}
##
options(na.action = "na.fail") 
refm <- dredge(refmodm,m.lim = c(1,4)) #note this, will take a few minutes to run

#View(subset(refm, delta <2 ))


sum_T1_RefS<-summary(model.avg(refm, subset = delta < 2))
#plot model output
df1_RefS<-as.data.frame(sum_T1_RefS$coefmat.full) #selecting full model coefficient averages

CI_RefS <- as.data.frame(confint(sum_T1_RefS, full=T)) # get confidence intervals for full model
df1_RefS$CI_RefS.min <-CI_RefS$`2.5 %` #pulling out CIs and putting into same df as coefficient estimates
df1_RefS$CI_RefS.max <-CI_RefS$`97.5 %`# order of coeffients same in both, so no mixups; but should check anyway
setDT(df1_RefS, keep.rownames = "coefficient") #put rownames into column

names(df1_RefS) <- gsub(" ", "", names(df1_RefS)) # remove spaces from column headers
```

## 2) Heatwave TRQ

### Model Selection

```{r, echo = `FALSE`}


require(MuMIn)
options(na.action = "na.fail")

#Refuge across heatwave conditions
modfactors_trqH <- factorsnum %>% drop_na(meanT_HW_surface)
modfactors_trqH_scaled<- modfactors_trqH %>% mutate_if(is.numeric, scale)%>% drop_na(meanT_HW_surface) 

# Model heatwave TRQ
refmodmHW<-lm(H_TRQ ~ perDD + SV + meanT + FNU + CC + CA + V, data=modfactors_trqH_scaled)

# Plot VIF values
vif_trqH<-vif(refmodmHW)
vif_trqH_df <- tibble::rownames_to_column(data.frame(vif_trqH), "coefficient")
ggplot(vif_trqH_df, aes(x=coefficient, y=vif_trqH)) +
  coord_flip()+
  geom_bar(stat = "identity")+
  geom_hline(yintercept = 5.0,linetype="dashed", color = "red")
```

### Model Residuals

```{r, echo = `FALSE`}
###############################################################################################
# check model residuals
shapiro.test(rstandard(refmodmHW)) #low p-value indicates that the observed data is unlikely under the assumption it was drawn from a normal distribution.
modfactors_trqH_scaled$residual <- refmodmHW$residuals
test1<-qplot(refmodmHW$fitted, refmodmHW$residuals,
             geom = "point") +
  geom_abline(intercept = 0,
              slope = 0,
              colour = "red") +
  labs(title = "Plot of residuals vs fitted values",
       x = "fitted value",
       y = "residual")
# Make a histogram of the residuals
test2<- qplot(refmodmHW$residuals,
              geom = "histogram",
              bins = 10) +
  labs(title = "Histogram of residuals",
       x = "residual")
test3<-ggplot(data = modfactors_trqH_scaled, aes(sample = residual)) +
  geom_qq() +
  geom_qq_line(colour = "red") +
  labs(title = "Quantile plot of residuals")
grid.arrange(test1,test2,test3)
###############################################################################################
```

### Model Results

```{r}
options(na.action = "na.fail")
heatmHW <- dredge(refmodmHW) #note this, will take a few minutes to run

top_model<-get.models(heatmHW, subset = 1)[[1]]
sum_T1_RefHW<-summary(get.models(heatmHW, subset = 1)[[1]])

#plot model output
df1_RefHW<-as.data.frame(sum_T1_RefHW$coefficients) #selecting full model coefficient averages

CI_RefHW <- as.data.frame(confint(top_model)) # get confidence intervals for full model
df1_RefHW$CI_RefHW.min <-CI_RefHW$`2.5 %` #pulling out CIs and putting into same df as coefficient estimates
df1_RefHW$CI_RefHW.max <-CI_RefHW$`97.5 %`# order of coefficients same in both, so no mixups; but should check anyway
setDT(df1_RefHW, keep.rownames = "coefficient") #put rownames into column
names(df1_RefHW) <- gsub(" ", "", names(df1_RefHW)) # remove spaces from column headers
```

## TRQ Plots

```{r}

# Prepare and combine the Summer and Heatwave TRQ model dataframes
data_RefHW <- df1_RefHW %>% dplyr::rename(CI.min=CI_RefHW.min,CI.max=CI_RefHW.max)
data_RefHW$Condition <- "Heatwave"
data_RefHW <- data_RefHW  %>% dplyr::select(coefficient,Estimate,Std.Error,CI.min,CI.max,Condition)
data_RefS <- df1_RefS %>% dplyr::rename(CI.min=CI_RefS.min,CI.max=CI_RefS.max)
data_RefS$Condition <- "Summer"
data_RefS <- data_RefS  %>% dplyr::select(coefficient,Estimate,Std.Error,CI.min,CI.max,Condition)
comb_trq_test <- rbind(data_RefS,data_RefHW)


# Plot Summer and Heatwave TRQ model coefficients!
refuge_plot <- ggplot(data=comb_trq_test[2:nrow(comb_trq_test),], aes(x=coefficient, y=Estimate, colour=Condition))+ #again, excluding intercept because estimates so much larger
  geom_hline(yintercept=0, color = "gray",linetype="dashed", lwd=1.5)+ #add dashed line at zero
  geom_errorbar(aes(ymin=CI.min, ymax=CI.max), width=0, lwd=1.5,alpha=1,position=position_dodge(width=0.7)) +
  coord_flip(ylim = c(-1, 1)) + # flipping x and y axes
  geom_point(size=4,position=position_dodge(width=0.7)) +
  theme_light() + 
  scale_color_manual(values=c("#F06C00","#2C9CB0"))+
  scale_x_discrete(limit=c("CA","SV","CC","V","FNU","perDD","meanT"),labels = c( "Catchment","Surface Veg","Canopy Cover","Initial Volume", "Turbidity","Draw Down","Mean Temp")) +
  theme_light()+  
  ylab("Thermal Refuge Quality Coefficient") +
  theme(axis.title.y = element_blank(),plot.title = element_text(hjust = 0.5),axis.title=element_text(size=12),plot.tag = element_text(size = 17))+
  labs(tag = "A")
refuge_plot
```

## 3) Summer Temp

```{r, echo = `FALSE`}

modfactors_tempS <- factorsnum %>% drop_na(meanT)
modfactors_tempS_scaled<- modfactors_tempS %>% mutate_if(is.numeric, scale)%>% drop_na(meanT) 

# Linear model of mean temperature
Tmodm<-lm(meanT ~ perDD + SV + FNU  + CC  + CA + V, data=modfactors_tempS_scaled)
```

### Model Residuals

```{r, echo = `FALSE`}
###############################################################################################
shapiro.test(rstandard(Tmodm)) #low p-value indicates that the observed data is unlikely under the assumption it was drawn from a normal distribution.
modfactors_tempS_scaled$residual <- Tmodm$residuals
# check model residuals
test1<-qplot(Tmodm$fitted, Tmodm$residuals,
             geom = "point") +
  geom_abline(intercept = 0,
              slope = 0,
              colour = "red") +
  labs(title = "Plot of residuals vs fitted values",
       x = "fitted value",
       y = "residual")
# Make a histogram of the residuals
test2<- qplot(Tmodm$residuals,
              geom = "histogram",
              bins = 10) +
  labs(title = "Histogram of residuals",
       x = "residual")
test3<-ggplot(data = modfactors_tempS_scaled, aes(sample = residual)) +
  geom_qq() +
  geom_qq_line(colour = "red") +
  labs(title = "Quantile plot of residuals")
grid.arrange(test1,test2,test3)
###############################################################################################
```

### Model Results

```{r, echo = `FALSE`}
##average top models

options(na.action = "na.fail") 
TmS <- dredge(Tmodm) #note this, will take a few minutes to run

#View(subset(TmS, delta <2 ))

sum_T1_TmS<-summary(model.avg(TmS, subset = delta < 2))
#plot model output
df1_TmS<-as.data.frame(sum_T1_TmS$coefmat.full) #selecting full model coefficient averages

CI_TmS <- as.data.frame(confint(sum_T1_TmS, full=T)) # get confidence intervals for full model
df1_TmS$CI_TmS.min <-CI_TmS$`2.5 %` #pulling out CIs and putting into same df as coefficient estimates
df1_TmS$CI_TmS.max <-CI_TmS$`97.5 %`# order of coeffients same in both, so no mixups; but should check anyway
setDT(df1_TmS, keep.rownames = "coefficient") #put rownames into column
names(df1_TmS) <- gsub(" ", "", names(df1_TmS)) # remove spaces from column headers
```

## 4) Heatwave Temp

```{r, echo = `FALSE`}
modfactors_tempH <- factorsnum %>% drop_na(meanT_HW)
modfactors_tempH_scaled<- modfactors_tempH %>% mutate_if(is.numeric, scale)%>% drop_na(meanT_HW) 

# Linear model of Heatwave mean temperature
TmodmHW<-lm(meanT_HW ~ perDD + SV + FNU + EV + CC + CA + V, data=modfactors_tempH_scaled)
```

### Model Residuals

```{r}
###############################################################################################
shapiro.test(rstandard(TmodmHW)) #low p-value indicates that the observed data is unlikely under the assumption it was drawn from a normal distribution.
modfactors_tempH_scaled$residual <- TmodmHW$residuals
# check model residuals
test1<-qplot(TmodmHW$fitted, TmodmHW$residuals,
             geom = "point") +
  geom_abline(intercept = 0,
              slope = 0,
              colour = "red") +
  labs(title = "Plot of residuals vs fitted values",
       x = "fitted value",
       y = "residual")
# Make a histogram of the residuals
test2<- qplot(TmodmHW$residuals,
              geom = "histogram",
              bins = 10) +
  labs(title = "Histogram of residuals",
       x = "residual")
test3<-ggplot(data = modfactors_tempH_scaled, aes(sample = residual)) +
  geom_qq() +
  geom_qq_line(colour = "red") +
  labs(title = "Quantile plot of residuals")
grid.arrange(test1,test2,test3)
###############################################################################################
```

### Model Results

```{r, echo = `FALSE`}
##average top models

options(na.action = "na.fail") 
Tm <- dredge(TmodmHW) #note this, will take a few minutes to run

#View(subset(Tm, delta <2 ))
sum_T1_Tm<-summary(model.avg(Tm, subset = delta < 2))
#plot model output
df1_Tm<-as.data.frame(sum_T1_Tm$coefmat.full) #selecting full model coefficient averages

CI_Tm <- as.data.frame(confint(sum_T1_Tm, full=T)) # get confidence intervals for full model
df1_Tm$CI_Tm.min <-CI_Tm$`2.5 %` #pulling out CIs and putting into same df as coefficient estimates
df1_Tm$CI_Tm.max <-CI_Tm$`97.5 %`# order of coeffients same in both, so no mixups; but should check anyway
setDT(df1_Tm, keep.rownames = "coefficient") #put rownames into column
names(df1_Tm) <- gsub(" ", "", names(df1_Tm)) # remove spaces from column headers
```

## Mean Temp Plots

```{r}

# Prepare and combine the mean temperature model dataframes
data_TmHW <- df1_Tm %>% dplyr::rename(CI.min=CI_Tm.min,CI.max=CI_Tm.max)
data_TmHW$Condition <- "Heatwave"
data_TmS <- df1_TmS %>% dplyr::rename(CI.min=CI_TmS.min,CI.max=CI_TmS.max)
data_TmS$Condition <- "Summer"
comb_temp_test <- rbind(data_TmS,data_TmHW)


# Plot Mean Temp model coefficients!
temp_plot <- ggplot(data=comb_temp_test[2:nrow(comb_temp_test),], aes(x=coefficient, y=Estimate, colour=Condition))+ #again, excluding intercept because estimates so much larger
  geom_hline(yintercept=0, color = "gray",linetype="dashed", lwd=1.5)+ #add dashed line at zero
  geom_errorbar(aes(ymin=CI.min, ymax=CI.max), width=0, lwd=1.5,alpha=1,position=position_dodge(width=0.5)) +
  coord_flip(ylim = c(-1, 1)) + # flipping x and y axes
  geom_point(size=4,position=position_dodge(width=0.5)) +
  theme_light() + 
  scale_color_manual(values=c("#F06C00","#2C9CB0"))+
  scale_x_discrete(limit=c("V","SV","CC"),labels = c("Initial Volume", "Surface Veg", "Canopy Cover")) +
  theme_light()+  
  ylab("Temperature Coefficient") +
  theme(axis.title.y = element_blank(),plot.title = element_text(hjust = 0.5),axis.title=element_text(size=12),plot.tag = element_text(size = 17))+
  labs(tag = "B")
temp_plot
```

## Final Figure

```{r}

# Arrange the TRQ and Mean Temperature plots
factor_plots_comb <- ggarrange(refuge_plot,temp_plot,common.legend = TRUE, legend="right",ncol=1,nrow=2)

# Save Plots
ggsave("factor_plots_comb.pdf", plot= factor_plots_comb,width = 12, height = 15, units = "cm")
factor_plots_comb
```

## Check Correlation Between TRQ and Temp

```{r}
# HEATWAVE CONDITIONS

TRQ_trq_summary <- modfactors_trqH %>% summarise(max_HW_TRQ = max(H_TRQ), min_HW_TRQ = min(H_TRQ), median_HW_TRQ = median(H_TRQ))

TRQ_temp_summary <- modfactors_trqH %>% summarise(max_HW_temp = max(meanT_HW), min_HW_temp = min(meanT_HW), median_HW_temp = median(meanT_HW))

## Surface
summary(aov(H_TRQ ~ meanT_HW_surface, data=modfactors_trqH))
cor(modfactors_trqH$H_TRQ, modfactors_trqH$meanT_HW_surface, method = "pearson")

## Bottom
summary(aov(H_TRQ ~ meanT_HW_bottom, data=modfactors_trqH))
cor(modfactors_trqH$H_TRQ, modfactors_trqH$meanT_HW_bottom, method = "pearson")


# SUMMER

summer_trq_summary <- modfactors_trqS %>% summarise(max_S_TRQ = max(TRQ), min_S_TRQ = min(TRQ), median_S_TRQ = median(TRQ))

summer_temp_summary <- modfactors_trqS %>% summarise(max_S_temp = max(meanT), min_S_temp = min(meanT), median_S_temp = median(meanT))

## Surface
summary(aov(TRQ ~ meanT_surface, data=modfactors_trqS))
cor(modfactors_trqS$TRQ, modfactors_trqS$meanT_surface, method = "pearson")

## Bottom
summary(aov(TRQ ~ meanT_bottom, data=modfactors_trqS))
cor(modfactors_trqS$TRQ, modfactors_trqS$meanT_bottom, method = "pearson")

ggplot(modfactors_trqH, aes(x=meanT_HW_bottom,y=H_TRQ)) + geom_point()
```
